Analyzing Toronto Island Ferry Ticket Counts

### 2024-09-24 paper/paper.qmd
edit paper

---
title: "Analyzing Toronto Island Ferry Ticket Counts"
subtitle: "A Statistical Exploration of Sales Trends"
author: 
  - Yingke He
thanks: "Code and data are available at: https://github.com/ohyykk/ferrySale.git"
date: 09-22-2024
date-format: long
abstract: "This study examines the ticket redemption and sales counts for the Toronto Island Ferry. We analyze time-based trends, relationships between sales and redemptions, and develop statistical models to predict ferry ticket usage. The results provide insights into usage patterns, highlight operational considerations, and suggest avenues for future research."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analyzing Toronto Island Ferry Ticket Counts"
subtitle: "A Statistical Exploration of Sales Trends"
author: 
  - Yingke He
thanks: "Code and data are available at: https://github.com/ohyykk/ferrySale.git"
date: 09-23-2024
date-format: long
abstract: "This study examines the ticket redemption and sales counts for the Toronto Island Ferry. We analyze time-based trends, relationships between sales and redemptions, and develop statistical models to predict ferry ticket usage. The results provide insights into usage patterns, highlight operational considerations, and suggest avenues for future research."
format: pdf
number-sections: true
bibliography: references.bib
---
